LSST Alerts: A Scientific Perspective on Packet Contents and Pre-Filtering

### 2020-02-28 draft-alertcontents.tex
update

\S~\ref{sec:packets} discusses how removing stamps and histories from alerts could be scientifically beneficial for some brokers, as long as stamps are made publicly available with similar latency, and proposes additional alert elements to better identify potential transient host galaxies.
\S~\ref{sec:prefilter} lists types of pre-filtered streams that could improve brokers' scientific productivity and estimates the resulting bandwidth reductions, and \S~\ref{sec:graceful} argues that when alerts are delayed, the scientifically optimal response would be to flag and distribute them as soon as possible (and not, e.g., send them directly to an archive).

>>>>

\S~\ref{sec:packets} discusses how removing stamps and histories from alerts could be scientifically beneficial for some brokers, as long as stamps are made publicly available with similar latency.
\S~\ref{sec:prefilter} lists types of pre-filtered streams that could improve brokers' scientific productivity and estimates the resulting bandwidth reductions, and \S~\ref{sec:graceful} argues that when alerts are delayed, the scientifically optimal response would be to flag and distribute them as soon as possible (and not, e.g., send them directly to an archive).
